---
title: "data analysis using dplyr"
author: "20122011_thomaskutty"
date: "01/01/2021"
output: word_document
---
## Data Analysis using Dyplr
```{r fig.height=3, fig.width=3, message=FALSE, warning=FALSE}
library(dplyr)
library("nycflights13")
df = flights
head(df)
```

Getting the summary of df 

```{r}
summary (df)
```

filter() and slice()
arrange()
select() and rename()
distict()
mutate() and transmute()
summarise()
sample_n() and sample_frac()


```{r}
filter(df,month ==11, day == 3, carrier == "AA")
```


using bracket notation 
```{r}
df[df$month == 11 & df$day ==3 & df$carrier == "AA" , ]
```

```{r}
slice (df, 1:7)
```


ordering the data using arrange function in dyplr
```{r}
head(arrange(df, year, month, day, arr_time))
```

descending ordering 
```{r}
head(arrange(df, month, desc(day)))
```

selecting columns 
```{r}
head(select(df, carrier,arr_time))
```
renaming columns 
```{r}
head(rename(df, MONTH = month ))
```


getting the distinct values 
```{r}
distinct(select(df, carrier))
```


mutate function : adding new columns using existing columns 

```{r}
head(mutate(df, new_col = arr_delay*dep_delay))
```

transmute function only returns the new column created
```{r}
head(transmute(df, new_col = arr_delay*dep_delay))
```

summarise function 
```{r}
summarise(df, avg_air_time = mean(air_time, na.rm = TRUE)) 
```
```{r}
summarise(df, total_time = sum(air_time, na.rm = TRUE)) 
```


Taking samples of dataframe
10 random samples 
```{r}
sample_n(df, 10)
```


splitting the dataframe using fractions 
```{r}
train = sample_frac(flights,0.80)
train 
```

```{r}
print(dim(df))
print(dim(train))
```


